\documentclass[letterpaper,twoside,11pt,headings=small]{scrartcl}

\PassOptionsToPackage{hang,small}{caption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{subfig}
\usepackage{fancyvrb}
\usepackage{booktabs}
\usepackage{xspace}
\usepackage{scrpage2}
\usepackage{pgf,tikz}
\usetikzlibrary{calc}
\usetikzlibrary{arrows}
\usepackage{ulem}
\normalem
\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont[Ligatures={TeX}]{Times New Roman}
\setsansfont[Ligatures={TeX}]{Helvetica Neue}
\setmonofont[Scale=MatchLowercase]{Menlo}

\newcommand{\thetitle}{TWC: Medium: Automated Reverse Engineering of Commodity Software\xspace}

\pagestyle{scrheadings}
\clearscrheadfoot
\lohead{NSF 13-578 --- Secure and Trustworthy Cyberspace}
\rohead{\pagemark}
\lehead{\thetitle}
\rehead{\pagemark}
\setheadsepline{0.5pt}
\setfootsepline{0pt}
\setkomafont{pageheadfoot}{\sffamily\fontsize{9}{9}\selectfont}
\setkomafont{pagenumber}{\sffamily\fontsize{9}{9}\selectfont}

\usepackage[unicode,bookmarks,colorlinks,breaklinks,pdftitle={},pdfauthor={}]{hyperref}
\hypersetup{linkcolor=black,citecolor=black,filecolor=black,urlcolor=black}

\begin{document}

\title{Data Management Plan}
\subtitle{\thetitle}
\author{}
\date{}
\maketitle

\section{Data Management Plan}
\label{sec:dmp}

In the following, we describe the plan for managing the data used and produced
as part of the proposed project.

\subsection{Project Description}
\label{sec:dmp:desc}

The goal of this project is to investigate techniques and implement tools for
automated whole-system understanding of closed-source software systems.  The
project leverages a scalable and precise dynamic analysis framework that operates
directly over binary code to enable automatic structure decomposition and generate
behavioral models and program summaries.  The system will facilitate applications
such as the proposed encrypted protocol fuzzing capability.

\subsection{Survey of Existing Data}
\label{sec:dmp:survey}

The project will require the acquisition, storage, and analysis of closed-source
software systems such as embedded firmware and user-level programs in binary form.
The collection process will respect the relevant software licenses and intellectual
property agreements covering these artifacts.

\subsection{Data to be Created}
\label{sec:dmp:created}

Analysis of the software artifacts to be collected will result in execution
traces, behavior models, and other derived summaries regarding the properties
of those artifacts.  The project will likely result in the discovery of
previously unknown vulnerabilities and potentially exploits for those
vulnerabilities.  Extreme caution will be exercised in order to prevent the
leakage of this information to unauthorized parties, and responsible
disclosure practices will be followed when notifying relevant parties of our
findings.

\subsection{Data Administration Issues}
\label{sec:dmp:admin}

\subsubsection*{Funding and Legislative Requirements}

All prototypes produced in the course of this project will be licensed under
an appropriate open source license, and copyright will be assigned if requested.

As noted above, licensing and intellectual property agreements will be respected
in all aspects of the project.

\subsubsection*{Data Owners and Stakeholders}

All data sets created as part of this project will be considered in the public
domain, and will be responsibly disclosed to interested researchers if
requested, unless legal agreements such as a non-disclosure agreement prevent
this.

\subsubsection*{File Formats and Standards}

Data will be collected and stored in accessible formats, and the necessary
code to manipulate the data will be provided upon request.  Source code for
the tools developed will be published in standard source code repositories
such as subversion, git, or mercurial.

\subsubsection*{Access and Security}

Access to all data will be strictly monitored and controlled.  Write access to
repositories of test artifacts, generated data, and project source code will
be restricted to collaborators and affiliated research personnel.  Read-only
access will be provided as needed, in accordance with the data sharing
requirements outlined above.

\subsection{Data Organization Methods}

\subsubsection*{Backups}

Standard services for automated backups and off-site replication will be
leveraged for the project data.  Data that is not under the direct physical
control of an authorized project collaborator will be encrypted using standard
best practices.

\subsubsection*{Other}

Source code for all research prototypes will be published using standard
source code repository software.  As a consequence, revision history will
be maintained for all software developed as part of the project.

\subsection{Data Sharing and Archiving}

Data will be publically sharable to appropriate parties if it is accordance
with legal requirements.  Data will be shared using standard network-based
mechanisms appropriate to the situation -- e.g., published via a web server
or provided via an encrypted channel.

All data will be archived for a period of at least seven years following
the completion of the project.

\subsection{Responsibilities}

The PI will be responsible for the above listed items.

\subsection{Budget}

All costs associated with the data management plan outlined above are
accounted for in the project budget.

\end{document}
